Reproducible development environments with rix

### 2023-12-23 paper.qmd
added overwrite equals T

rix(r_ver = "4.3.1",
    project_path = tempdir(),
    print = TRUE)
```

@@

rix(r_ver = "4.2.2",
    r_pkgs = c("dplyr", "chronicler"),
    project_path = tempdir(),
    print = TRUE)
```

>>>>

rix(r_ver = "4.3.1",
    project_path = tempdir(),
    overwrite = TRUE,
    print = TRUE)
```

To define a variable in the [Nix]{.proglang}, the `let` keyword is used, so
the first lines of this expression define a variable called `pkgs` and
`system_pkgs`. `pkgs` is defined as the set of packages to be used in
this derivation. In this example, the package expressions are going to be pulled
from the `nixpkgs`

@@

rix(r_ver = "4.2.2",
    r_pkgs = c("dplyr", "chronicler"),
    project_path = tempdir(),
    overwrite = TRUE,
    print = TRUE)
```
